Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-20 doc/manuscript/ESSDmanuscript.Rmd
knit in new table
#36

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. ") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)  %>%
  row_spec(1, bold = TRUE)  %>% #biomass
  row_spec(6, bold = TRUE)  %>% #agb
  row_spec(14, bold = TRUE) %>% #root
  row_spec(25, bold = TRUE)  %>% #dead wood
  row_spec(33, bold = TRUE)  %>% #litter
  row_spec(40, bold = TRUE)  %>% #som
  row_spec(44, bold = TRUE)  #total
```

>>>>

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table[,-1], format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. ") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)  %>%
  row_spec(which(C_variables_table$bold), bold = TRUE) #total
```
